%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Eric Spencer} \\ \vspace{1pt}
    \small \href{mailto:ericspencer1450@gmail.com}{\underline{ericspencer1450@gmail.com}} $|$ 
    \href{https://ericspencer00.github.io}{\underline{ericspencer00.github.io}} $|$
    \href{https://linkedin.com/in/ericspencer00}{\underline{linkedin.com/in/ericspencer00}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Loyola University Chicago}{Chicago, IL}
      {Bachelor of Science in Computer Science, Minor in Information Systems}{Expected May 2026}
      \resumeItemListStart
        \resumeItem{Dean’s List: Fall 2023, Spring 2024, Fall 2024}
        % \resumeItem{Trustee Scholarship recipient}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Software Engineering Intern}{January 2025 -- Present}
      {EpiFinder Medical Solutions}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Develop software solutions to optimize medical clinic operations and workflows.}
        \resumeItem{Design and implement internal tools to improve staff efficiency and patient care.}
        \resumeItem{Gain hands-on experience in understanding and addressing the technical needs of a medical clinic.}
      \resumeItemListEnd

    \resumeSubheading
      {ITS Service Desk Technician}{July 2024 -- Present}
      {Loyola University Chicago}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Resolve over 50 support tickets weekly, ensuring prompt and effective resolutions to user issues.}
        \resumeItem{Utilize Azure and BI tools to verify identity and grant secure access.}
        \resumeItem{Collaborate with backend teams to address complex customer challenges.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Undergraduate Research Assistant}{April 2023 -- August 2023}
      {Loyola University Chicago}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Investigated AI interpretability through a research study analyzing ChatGPT's handling of advanced Java concepts.}
        \resumeItem{Collaborated with professors and peers to document findings and refine methodologies.}
      \resumeItemListEnd

    \resumeSubheading
      {Honor Caddie}{Seasonal 2017 -- 2024}
      {Oak Park Country Club}{River Grove, IL}
      \resumeItemListStart
        \resumeItem{Provided a customer-focused experience while supporting players with on-course decision-making.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
         \resumeProjectHeading
          {\textbf{Health-Up App} $|$ \emph{Java, Swift, React Native, RESTful APIs}}{}
          \resumeItemListStart
            \resumeItem{Built a fitness app leveraging nutrition and workout data using public APIs in collaboration with another programmer.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Movie Recommendation Model} $|$ \emph{Flask, Tensorflow, BeautifulSoup}}{}
          \resumeItemListStart
            \resumeItem{Hosted a recommendation model using Heroku, integrating data from Letterboxd.}
            \resumeItem{Optimized API calls to ensure performance within a 30-second limit for user-facing interactions.}
          \resumeItemListEnd
        
      \resumeProjectHeading
          {\textbf{Dexcom Alerts System} $|$ \emph{MySQL, Matplotlib}}{}
          \resumeItemListStart
            \resumeItem{Developed an alert system for critical glucose levels, ensuring timely notifications.}
            \resumeItem{Designed data integration pipelines for long-term statistical analysis beyond 24-hour CGM data.}
          \resumeItemListEnd


      \resumeProjectHeading
          {\textbf{Google AI Cloud Computing Hackathon} $|$ \emph{Vertex AI}}{}
          \resumeItemListStart
            \resumeItem{Developed a machine learning prediction model to classify whether a current Major League Baseball player would be inducted to the Hall of Fame.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EXTRACURRICULARS-----------
\section{Extracurriculars}
\resumeSubHeadingListStart
    \resumeSubheading
      {Vice President of Technology}{Fall 2024 – Spring 2025}{Loyola AI Club}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Manage and coordinate semester-long projects, enhancing members' technical and collaborative skills.}
      \resumeItemListEnd
    

    % \resumeSubheading
    %   {IT Chair}{Spring 2024 -- Fall 2024}{Alpha Kappa Psi, Gamma Iota}{Chicago, IL}
    %   \resumeItemListStart
    %     \resumeItem{Developed and managed the organization's official website, ensuring its user experience and usability.}
    %   \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, Swift} \\
     \textbf{Technologies}{: MySQL, Azure, Heroku, Google Cloud} \\
     \textbf{Frameworks}{: React Native, Angular}\\
     \textbf{Tools}{: Git, Excel, Tableau, UNIX}
     
    }}
 \end{itemize}
%-------------------------------------------
\end{document}
